### 2014-03-03 seminar/seminar_report/chapter3.tex
changes

Web services come with different quality of service parameters.
These parameters with a short description are listed in Table
\ref{qosws}.

\begin{table}[!t]
\centering
\caption{List of web service QoS parameters.}
\begin{tabular}{|c|c||c|c|}
\hline
\textbf{Parameter} & \textbf{Definition} \\
\hline\hline
$Availability$ & Probability of being available during \\
&a time frame \\
$Reliability$ & Probability of successfully handling \\
&requests during a timeframe\\
$Successability$ & Rate of successfully handled requests \\
$Throughput$ & Average rate of handling requests \\
$Latency$ & The average latency of services\\
$Capacity$ & Amount of resources available\\
$Cost$ & Mean service fee \\
$Regulatory$ & Compliance with standards, law and rules\\
$Security$ & Quality of confidentiality \\
&and non-repudiation\\
\hline
\end{tabular}
\label{qosws}
\end{table}

We adopted a real world dataset \cite{DBLP:conf/smc/Al-MasriM09a}
which has aggregated and normalized each of these parameters to a
real value between 0 and 1. Since requests are not shared among
web services and are distributed among all of them inside a
community, each one of them comes with a given QoS denoted by
$(QoS_{ws})$. We assume that $(QoS_{ws})$ is obtained by a certain
aggregation function of the parameters considered in Table
\ref{qosws}. We use this quality output later in evaluating the
community \emph{worth} or \emph{payoff} function.

@@

\begin{figure*}[!t]
\centerline{\includegraphics[width=15cm]{Figures/archss.eps}}
\caption{Architecture of Web Service communities}
\label{fig_community}
\end{figure*}

@@

The communities and web services earn revenue by performing tasks.
The total gain is function of quality ($QoS_{ws}$) and throughput
($Th_{ws}$) of tasks being performed. As mentioned in section
\ref{ws_parameters}, $QoS_{ws}$ is obtained by a certain
aggregation function of the parameters considered in Table
\ref{qosws}. We have adopted a linear equal weight average over
all QoS parameters listed in Table \ref{qosws} excluding the
$Throughput$ and $Cost$ parameters. A community has the option to
weigh specific QoS parameters depending on the expectations of
their clients.

@@

In this first scenario, we only consider one grand coalition and
analyze the system from the point of view of one single master web
service and a collection of web services. The master web service
decides which members can join
%or should leave%
the community and distributes the requests and income among its
community members (see Figure \ref{fig_sim1}).

\begin{figure}[!t]
\centering
\includegraphics[width=3in]{Figures/s1.eps}`
\caption{Web Services and A Grand Community}
\label{fig_sim1}
\end{figure}

The membership decision is made based on throughput and \emph{QoS}
of the considered web service. The goal is to have quality web
services in the community so it stays stable and no other web
services would have incentives to deviate and leave the coalition
$C$. Therefore, a basic method would be to check the core of the
coalition $C$ considering all the current community members (all
web services already residing within the community) and the new
web service. This algorithm uses the \emph{Shapley value}
distribution method as described in Equation \ref{eq:shapley} to
distribute the gain of $v(C)$ among all the members and then
checks if the \emph{Shapley value} payoff vector for this
community having the characteristic function $v(C)$ is in the
\emph{core}. In the \emph{Shapley value} payoff vector, the payoff
for each web service $ws_i$ is calculated based on its marginal
contribution $v(C \cup {i}) - v(C)$ over all the possible
different permutations in which the coalition can be formed, which
makes the payoff distribution fair. Because of going through all
the possible permutations of subsets of $N$, the nature of the
\emph{Shapley value} is combinatorial, which makes it impractical
to use as the size of our coalitions grows. However, it is proven
that in convex games, the \emph{Shapley value} lies in the core
\cite{DBLP:conf/ijcai/GrecoMPS11, myerson1991game}. Thus, if the
\emph{Core} is non-empty, the payoff vector is a member of the
\emph{Core}. The following proposition is important to make our
algorithm tractable.
% so in our algorithm we check the core membership of this payoff vector.

%\ref{eq:convex}.

%\newtheorem{theorem}{Proposition}
%\begin{theorem}[Einstein-Podolsky-Rosenberg]
\begin{theorem}\label{proposition1}
A game with a characteristic function $v$
is convex if and only if for all $S$, $T$, and $i$ where $S
\subseteq T \subseteq N \backslash \left\{i\right\}, \forall i \in
N$,
%For $\forall S \subseteq T \subseteq N \backslash \left\{i\right\}, \forall i \in N$ we have:
\begin{equation}\label{eq:convex_snow}
v(S \cup \left\{i\right\}) - v(S) \leq v (T \cup \left\{i\right\}) - v(T)
\end{equation}
\end{theorem}

%\begin{Proposition}\label{proposition} A game with a characteristic function $v$
%is convex if and only if for all $S$, $T$, and $i$ where $S
%\subseteq T \subseteq N \backslash \left\{i\right\}, \forall i \in
%N$,
%For $\forall S \subseteq T \subseteq N \backslash \left\{i\right\}, \forall i \in N$ we have:
%\begin{equation}\label{eq:convex_snow}
%v(S \cup \left\{i\right\}) - v(S) \leq v (T \cup \left\{i\right\}) - v(T)
%\end{equation}
%\end{Proposition}

\begin{proof}
We first prove the ``only if'' direction:
%\\$~~~~$\textbf{1}. ``only if'' direction:\\
\\$~~~~$\ \textbf{1}. ``only if'' direction:\\
%\setlength{\abovedisplayshortskip}{2pt}
Assume:\\
\vspace{-0.5cm}
\begin{gather*}\label{convexsnowproof}
v(S \cup \left\{i\right\}) - v(S) \leq v (T \cup \left\{i\right\})
- v(T)
\\
\rightarrow v(S \cup \left\{i\right\}) + v(T) \leq v (T \cup \left\{i\right\}) + v(S)
\end{gather*}

Considering $S \subseteq T$:
\setlength{\abovedisplayshortskip}{2pt}
\begin{gather*}
T \cup \left\{i\right\} = (S \cup \left\{i\right\}) \cup T
\\
S = (S \cup \left\{i\right\}) \cap T
\end{gather*}

By setting $A = S \cup \left\{i\right\}$ and $B = T$ we have:
\setlength{\abovedisplayshortskip}{2pt}
\begin{gather*}
v(S \cup \left\{i\right\}) + v(T) \leq v (T \cup \left\{i\right\}) + v(S)
\\
\rightarrow v(S \cup \left\{i\right\}) + v(T) \leq
\\
v((S \cup \left\{i\right\}) \cup T) + v((S \cup \left\{i\right\}) \cap T)
\\
\rightarrow v(A) + v(B) \leq v(A \cup B) + v(A \cap B)
\end{gather*}
Consequently, the game is convex.

\textbf{2}. ``if'' direction:\\
Assume the game is convex. Thus, for all $A, B \subset N$, we
have: \setlength{\abovedisplayshortskip}{2pt}
\begin{gather*}
v(A) - v(A \cap B) \leq v(A \cup B) - v(B)
\end{gather*}

By setting $S \cup \left\{i\right\} = A$ and $T = B$ where $S \subseteq T$:
\setlength{\abovedisplayshortskip}{2pt}
\begin{gather*}
v(S \cup \left\{i\right\}) - v((S \cup \left\{i\right\}) \cap T) \leq v(T \cup (S \cup \left\{i\right\})) - v(T)
\\
\rightarrow v(S \cup \left\{i\right\}) - v(S) \leq v(T \cup \left\{i\right\}) - v(T)
\end{gather*}

\end{proof}

Thus, in order to keep the characteristic function convex, new web
services should have more marginal contribution as the coalition
size grows.

Our algorithm works as follows. Given an  established community
with a master and some member web services, a web service would send a \emph{join request} to join  the
community. Ideally, the \emph{core}
or \emph{$\epsilon$-core} stability of the group having this new
member should be analyzed. As the normal core membership algorithm is computationally
intractable, we exploit Proposition \ref{proposition1} and Equation
\ref{eq:convex_snow} to check the convexity of our game having
characteristic function where the new member is added. In the
equation, let $C$  be our community members before
having the new web service join the community. Let  ${i}$ be the new web
service, and then verify the equation for $S$, setting $ S = T /
W1 $ where $W1$ is the set of all possible subsets of the set $N$
having the size $1$. We can relax the equation a bit by adding a
constant $\epsilon$ to the left side of the equation. We call this
method \emph{Depth-1 Convex-Checker} algorithm. If the equation is
satisfied for all $W1$, we let the new web service join our
community, since the web service will contribute positively enough
to make our new community stable. Since only subsets of size $1$
are checked, the following Proposition holds.

\begin{theorem}\label{complexity1}
\emph{The run time complexity of Depth-1 Convex-Checker algorithm is
$O(n)$.}
\end{theorem}

By this result, we obtain a significant reduction from $O(2^n)$,
which is the complexity of checking all possible subsets of $N$.
In our second method, we use the same algorithm, but this time we
set $W2$ to be the set of all possible subsets of size two and one
of the community $C$. We call this method \emph{Depth-2
Convex-Checker} and its run time complexity is still
linear:

\begin{theorem}\label{complexity2}
\emph{The run time complexity of Depth-2 Convex-Checker algorithm is
$O(n^2)$.}
\end{theorem}

It is possible to develop an algorithm that continues the
verification of this condition against subsets of size $3$,
$4$, etc. until the algorithm gets interrupted.

@@

In this scenario, we consider multiple communities managed by
multiple master web services, each of which is providing
independent request pools (see Figure \ref{fig_sim2}). Identical
to the first scenario, master web services form coalitions with
web services. We use coalition structure formation methods to
partition web services into non-empty disjoint coalition
structures. As mentioned in Section \ref{sec:coalition}, the used
algorithms in \cite{Sandholm:1999:CSG:317145.317152,DBLP:conf/ijcai/GrecoMPS11,DBLP:conf/ijcai/RahwanMJ11} try to
solve key fundamental problems of what coalitions to form, and how
to divide the payoffs among the collaborators.

\begin{figure}[!t]
\centering
\includegraphics[width=3in]{Figures/s2.eps}
\caption{Web Services and Many Communities}
\label{fig_sim2}
\end{figure}

@@

This merge-and-split algorithm is designed to be adaptable to
different applications. One major ingredient to use such an
algorithm is a preference relation or well-defined orders proper
for comparing collections of different coalition partitions of the
same set of players. Having two partition sets of players, namely
$P = {P_1,...,P_k}$ and $Q = {Q_1,...Q_l}$, one example would be
to use the social welfare comparison $\sum^k_{i=1}v(P_i) >
\sum^l_{j=1}v(Q_j)$. For our scenario, we use \emph{Pareto order}
comparison, which is an individual-value order appropriate for our
self-interest web services. In the Pareto order, an allocation or
partition $P$ is preferred over another $Q$ if at least one player
improves its payoff in the new allocation and all the other
players still maintain their payoff ($p_i \geq q_i$ with at least
one element $p_i > q_i$).

The valuation function $v(C)$ for this scenario is the same as
\emph{``Web Services and One Community''} scenario. However, in
order to prevent master web services joining the same community,
we set $v(C) = 0$ when $C$ has either none, or more than one
master web service as member.

In this scenario, as new web services are discovered and get ready
to join communities, our algorithm keeps merging and splitting
partitions based on the preference function. The decision to merge
or split is based on the fact that all players must benefit. The
new web services will merge with communities if $all$ the players
are able to improve their individual payoff, and some web services
may split from old communities, if splitting does not decrease the
payoff of \emph{any} web service of the community. According to
\cite{DBLP:journals/corr/abs-cs-0605132}, this sequence of merging
and splitting will converge to a final partition, where web
services cannot improve their payoff. More details of this
algorithm and analysis of generic solutions on coalition formation
games are described in \cite{DBLP:journals/igtr/AptW09}.

@@

Figure \ref{architectureFigure} illustrates the architecture of a
typical community aggregating a number of services with different
interactive strategies. Some of them compete for the task where
they directly deal with the master. Some others cooperate in the
associated task where they only deal with the competed service as
the task leader and do not directly interact with the master (the
master deals only with the service that has bid for the task,
which is responsible of choosing its collaborative network). In
both sets, some service agents are for certain moments out of any
collaboration network. We highlight details of the interactive
strategies in the rest of this section.
%Figure \ref{algorithm1} %exposes the details of task allocation mechanism that is used to select the web services.
In the proposed system, the master sorts the competing services
(i.e., the bidders) based on some parameters (such as reputation)
that we explain in the rest of this section. The winner to which
the master allocates the task is the bidder
service agent that is ranked first. %If the web
%service is busy or unwilling to take the task, the master
%allocates the task to the second competing web service in the
%list.
There is a chance that some tasks could not be assigned to any
service. These tasks are accumulated in the task pool to be
allocated in the next task allocation round. Upon allocation of
the task, the service is responsible for offering the required QoS
that is stated in the task being generated by a consumer.
Afterwards,  the master rewards or penalizes the competing
service by upgrading or degrading its reputation according to the
offered QoS compared with the required one. This comparison
influences the sorting mechanism used by the master to allocate
the tasks in further task allocation rounds.

@@

The assigned reputation value is updated by the computed reward
value. The computed reputation of services is bounded by the
minimum and maximum reputation values $0$ and $1$. % to constrain
%the balance the cooperative community of web services. The updated
Let $\Gamma = Rep_{w}^{t} + reward_w^t$. The updated reputation
value is then computed as follows:

\begin{equation}\label{repz}
%Rep_{w}^{t+1} = Rep_{w}^{t} + reward
%\end{equation}
%\begin{equation*}
Rep_{w}^{t+1} = \begin{cases}

\Gamma & \text{if $ 0 \leq \Gamma \leq 1$;}\\
0  & \text{if $\Gamma < 0$;}\\
1 & \text{if $\Gamma > 1$.}\\
\end{cases}
\end{equation}
%
For new services with no previous reputation value, we use the
bootstrapping trust technique proposed in \cite{conf/icwe/YahyaouiZ11}. This
technique consists in giving the new services a chance and observe
their behaviors for a period of testing time. The observation
sequence is modeled as a hidden Markov model that is used to
detect the behavior of the service by comparing the observation
behavior against pre-defined trust patterns. Based on the matching
result, an initial value is assigned to the service. Using this
initial reputation value, services quickly converge to their
actual and stable values using the update function.

\begin{proposition}\label{Complexity-Rep}
$Rep_{w}^{t}$ can be computed in time $O(|t|)$, i.e., in time
linear in the size of the window $t$.
\end{proposition}

\begin{proof}\footnote{In this paper, we
assume that the common arithmetic and elementary functions, such
as multiplication, division and trigonometric functions can be
computed in time $O(1)$ as they operate on inputs of fixed sizes.}
The function $Rep_{w}^{t}$ is recursive on $t$, but the algorithm
works by storing the last calculated reputation value in a
variable, so it will not be recalculated again at each iteration.
However, the calculation of $reward_w^t$ is needed. Since the
function $reward_w^t$ can be computed in time linear in the number
of tasks (see Equations \ref{repr} and \ref{reward}), which in
turn is linear in the size of the window time, the result follows.
$\Box$
\end{proof}

\textbf{Growth Factor} ($G_w^t$) is a parameter which declares
services' performance based on their recent strategies and
activities. Growth factor is relative to services' reputation
$Rep_w^t$, QoS during the window time $t$ $QoS_w^t$, and budget
$B_w^t$. This factor is the main variable a typical service uses
to decide about which strategy to adopt. The details about the
decision making process are described in Section \ref{Theoretical
Results}. We use Equation \ref{eq:growthfactor} to compute the
growth factor $G^t_w$ of the service $w$ during the window time
$t$ as the average of the three aforementioned parameters, where
$n_t$ is the total number of offered tasks to the whole community
during the
window time $t$, %(we consider the time window $t$ large enough so
%that $n_t \neq 0$),
$\mu_w$ is the mean received service fee, and $\epsilon$ is the
cost of community membership.

@@

This equation is designed so that it satisfies the following
desirable properties:

\begin{enumerate}

\item The growth factor function should be monotonically
increasing in the offered quality of service $QoS_w^t$.

\item The growth factor function should be monotonically
increasing in the service's reputation $Rep^t_w$.

\item The growth factor function should be monotonically
increasing in the budget $B_w^t$ if the maximum possible profit is
positive and monotonically decreasing in $B_w^t$ if the maximum
possible profit is negative. This property reflects the idea that
the budget contributes in the increase of the growth factor as far
as there is a chance to make profit. In fact, the contribution of
the budget $B_w^t$ in the calculation of the growth factor should
be proportional to the maximum possible profit $n_t \mu_w -
\epsilon$ where the service $w$ receives all the offered tasks
during the window time $t$.

\end{enumerate}

  % if the profit $\beta_w$ made by the web service $w$
%considering the mean received service fee $\mu_w$ and the cost of
%community membership $\epsilon$ is positive.
It is easy to show that Equation \ref{eq:growthfactor} satisfies
the three aforementioned properties by calculating the partial
derivatives $\partial G^t_w$ of this function in 1) $QoS_w^t$
($\frac{\partial G^t_w}{\partial QoS_w^t} = \frac{1}{3} $); 2)
$Rep^t_w$ ($\frac{\partial G^t_w}{\partial Rep^t_w} = \frac{1}{3}
$); and 3) $B_w^t$ ($\frac{\partial G^t_w}{\partial B_w^t} =
\frac{1}{3 (n_t \mu_w - \epsilon)} $). Thus, the sign of the two
first partial derivatives is positive and the sign of
$\frac{\partial G^t_w}{\partial B_w^t}$ depends on the sign of the
maximum profit $n_t \mu_w - \epsilon$, so we are done. The mean
service fee depends on the strategy adopted by the service because
a competitive service receives higher fees $\mu_{w, CM}$ compared
to a cooperative one $\mu_{w, CO}$ ($\mu_{w, CM} > \mu_{w, CO}$).
The motivation behind this is that a competitive service for a
given task is the leader for that task while other cooperative
services are performing specific subtasks as asked by the leader.

\begin{proposition}\label{Complexity-Growth_Factor}
$G_w^t$ can be computed in time linear in the size of the window
$t$.
\end{proposition}

\begin{proof}
As shown in the second part of Equation \ref{eq:growthfactor}, the
function $QoS_w^t$ can be computed in time linear in the number of
tasks, which in turn is linear in the size of the window time.
Since $B_w^t$ is constant, the result follows from Proposition
\ref{Complexity-Rep}. $\Box$
\end{proof}

@@

In this section, we discuss the experiments we performed for our
scenarios to validate the applicability and performance of our
proposed methods in realistic environments.
An XML SOAP based messaging system was implemented. The request
contains the flight dates, the origin and destination, type of
tickets, and number of guests. The response contains different
flights with different companies, prices, timing, etc. We have
gathered around 200,000 flights and stored them in our MongoDB
database. We created a pool of web services and populated most of
their \emph{QoS} parameters from a real world web service dataset
\cite{DBLP:conf/smc/Al-MasriM09a}\footnote[1]{The implemented
environment includes the QWS dataset by Eyhab Al-Masri and Qusay
H. Mahmoud freely available at:
http://www.uoguelph.ca/\textasciitilde{}qmahmoud/qws/.}. To test
our methods, we formed around 10,000 random coalitions consisting
of 3 to 160 web services. In average, the communities were populated by 60 web
services. Thus, in total, the number of used web services is
600,000. This makes our system scalable enough. We implemented the
scenarios using Java and executed the experiments on an Intel Xeon
X3450 machine with 6GBs of memory. For other parameters missing
from the dataset, we used normal random distribution with
parameters estimated using the method of maximum likelihood.

@@

For the \emph{optimal core} method, we have used the well known
\emph{$\epsilon$-core} method as the taxation method to relax the
core condition to help communities attract web services. We have
assigned $\epsilon$ to 15\% of total community worth, which means
$\epsilon = 0.15 \times v(C)$. This allows subsets of the
coalition to gain maximum 15\% of $v(C)$. In the \emph{optimal
$\epsilon$-core} method, we capped the coalition size to 25 web
services, since the method is computationally intractable as the
number of web services increases. In fact, given the machine
configuration we used in our experiments, the maximum number we
could run for this method is 25, which is very realistic if we
consider the real airlines coalitions (the three well known
coalitions have respectively 28, 19, and 13 members). In the other
methods, there were no cap on size of the community and we had
communities of size 160 web services at some points, as discussed
above. In the experiments, our \emph{Depth-1 Convex-Checker} and
\emph{Depth-2 Convex-Checker} methods generate results instantly
(0.01ms in Java millisecond time unit granularity) in our machines
since their runtime with respect to the size of input (number of
web services) is $O(n)$ and $O(n^2)$ respectively. This shows that
the algorithms are efficient and the system is easily scalable. In
this scenario, our community receives 130 tasks from users on
average per iteration. These tasks are about flight booking and
are expected to be performed by the community. They are randomly
generated using a poisson distribution (having 130 as parameter).
Depending on community task queue and the assigned web services'
quality metrics the task will be performed with some qualities.
The community, after the task distribution process on each
iteration, will reevaluate QoS metrics of its members and can
check for new membership requests. Web services may join or leave
the community between iterations. The results show that our
\emph{depth-2 convex checker} method is performing better compared
to the other methods and its performance is close to the optimal
\emph{$\epsilon$-core} method. Our \emph{depth-1 convex checker}
and the \emph{3-Way Satisfaction} method, are also performing
well.

\begin{figure*}%[!t]
\centering
%\includegraphics[scale=0.6]{graph1Final+.eps}
\includegraphics[width=3in]{least_core.eps}
\caption{Analysis of \emph{$\epsilon$-core} set non-emptiness for
different values of $\epsilon$} \label{f_leastcore}
\end{figure*}

>>>>

Web services come with different quality of service parameters.
These parameters include availability, reliability, successability, throughput, latency, capacity, cost, regulatory and security\cite{DBLP:conf/smc/Al-MasriM09a}.
We adopted a real world dataset \cite{DBLP:conf/smc/Al-MasriM09a}
which has aggregated and normalized each of these parameters to a
real value between 0 and 1. Since requests are not shared among
web services and are distributed among all of them inside a
community, each one of them comes with a given QoS denoted by
$(QoS_{ws})$. We assume that $(QoS_{ws})$ is obtained by a certain linear weight function of the parameters. We use this quality output later in evaluating the
community \emph{worth} or \emph{payoff} function.

@@

\begin{figure*}[!t]
\centerline{\includegraphics[width=15cm]{community.eps}}
\caption{Architecture of Web Service communities}
\label{fig_community}
\end{figure*}

@@

The communities and web services earn revenue by performing tasks.
The total gain is function of quality ($QoS_{ws}$) and throughput
($Th_{ws}$) of tasks being performed. We have adopted a linear equal weight average over
the QoS parameters excluding the
$Throughput$ and $Cost$ parameters. A community has the option to
weigh specific QoS parameters depending on the expectations of
their clients.

@@

In this first scenario, we only consider one grand coalition and
analyze the system from the point of view of one single master web
service and a collection of web services. The master web service
decides which members can join
%or should leave%
the community and distributes the requests and income among its
community members.

%\begin{figure}[!t]
%\centering
%\includegraphics[width=3in]{Figures/s1.eps}`
%\caption{Web Services and A Grand Community}
%\label{fig_sim1}
%\end{figure}

The membership decision is made based on throughput and \emph{QoS}
of the considered web service. The goal is to have quality web
services in the community so it stays stable and no other web
services would have incentives to deviate and leave the coalition
$C$. Therefore, a basic method would be to check the core of the
coalition $C$ considering all the current community members (all
web services already residing within the community) and the new
web service. This algorithm uses the \emph{Shapley value}
distribution method as described in Equation \ref{eq:shapley} to
distribute the gain of $v(C)$ among all the members and then
checks if the \emph{Shapley value} payoff vector for this
community having the characteristic function $v(C)$ is in the
\emph{core}. In the \emph{Shapley value} payoff vector, the payoff
for each web service $ws_i$ is calculated based on its marginal
contribution $v(C \cup {i}) - v(C)$ over all the possible
different permutations in which the coalition can be formed, which
makes the payoff distribution fair. Because of going through all
the possible permutations of subsets of $N$, the nature of the
\emph{Shapley value} is combinatorial, which makes it impractical
to use as the size of our coalitions grows. However, it is proven
that in convex games, the \emph{Shapley value} lies in the core
\cite{DBLP:conf/ijcai/GrecoMPS11, myerson1991game}. Thus, if the
\emph{Core} is non-empty, the payoff vector is a member of the
\emph{Core}. The following proposition is important to make our
algorithm tractable.

@@

In this scenario, we consider multiple communities managed by
multiple master web services, each of which is providing
independent request pools. Identical
to the first scenario, master web services form coalitions with
web services. We use coalition structure formation methods to
partition web services into non-empty disjoint coalition
structures. As mentioned in Section \ref{sec:coalition}, the used
algorithms in \cite{Sandholm:1999:CSG:317145.317152,DBLP:conf/ijcai/GrecoMPS11,DBLP:conf/ijcai/RahwanMJ11} try to
solve key fundamental problems of what coalitions to form, and how
to divide the payoffs among the collaborators.

%\begin{figure}[!t]
%\centering
%\includegraphics[width=3in]{Figures/s2.eps}
%\caption{Web Services and Many Communities}
%\label{fig_sim2}
%\end{figure}

@@

@@

Figure \ref{architectureFigure} illustrates the architecture of a
typical community aggregating a number of services with different
interactive strategies. Some of them compete for the task where
they directly deal with the master. Some others cooperate in the
associated task where they only deal with the competed service as
the task leader and do not directly interact with the master (the
master deals only with the service that has bid for the task,
which is responsible of choosing its collaborative network). In
both sets, some service agents are for certain moments out of any
collaboration network. Upon allocation of
the task, the service is responsible for offering the required QoS
that is stated in the task being generated by a consumer.
Afterwards,  the master rewards or penalizes the competing
service by upgrading or degrading its reputation according to the
offered QoS compared with the required one. This comparison
influences the sorting mechanism used by the master to allocate
the tasks in further task allocation rounds.

@@

The assigned reputation value is updated by the computed reward
value. The computed reputation of services is bounded by the
minimum and maximum reputation values $0$ and $1$. % to constrain
%the balance the cooperative community of web services. The updated
%Let $\Gamma = Rep_{w}^{t} + reward_w^t$. 
%The updated reputation
%value is then computed as follows:
%
%\begin{equation}\label{repz}
%%Rep_{w}^{t+1} = Rep_{w}^{t} + reward
%%\end{equation}
%%\begin{equation*}
%Rep_{w}^{t+1} = \begin{cases}
%
%\Gamma & \text{if $ 0 \leq \Gamma \leq 1$;}\\
%0  & \text{if $\Gamma < 0$;}\\
%1 & \text{if $\Gamma > 1$.}\\
%\end{cases}
%\end{equation}
%
%For new services with no previous reputation value, we use the
%bootstrapping trust technique proposed in \cite{conf/icwe/YahyaouiZ11}. This
%technique consists in giving the new services a chance and observe
%their behaviors for a period of testing time. The observation
%sequence is modeled as a hidden Markov model that is used to
%detect the behavior of the service by comparing the observation
%behavior against pre-defined trust patterns. Based on the matching
%result, an initial value is assigned to the service. Using this
%initial reputation value, services quickly converge to their
%actual and stable values using the update function.

%\begin{proposition}\label{Complexity-Rep}
%$Rep_{w}^{t}$ can be computed in time $O(|t|)$, i.e., in time
%linear in the size of the window $t$.
%\end{proposition}

%\begin{proof}\footnote{In this paper, we
%assume that the common arithmetic and elementary functions, such
%as multiplication, division and trigonometric functions can be
%computed in time $O(1)$ as they operate on inputs of fixed sizes.}
%The function $Rep_{w}^{t}$ is recursive on $t$, but the algorithm
%works by storing the last calculated reputation value in a
%variable, so it will not be recalculated again at each iteration.
%However, the calculation of $reward_w^t$ is needed. Since the
%function $reward_w^t$ can be computed in time linear in the number
%of tasks (see Equations \ref{repr} and \ref{reward}), which in
%turn is linear in the size of the window time, the result follows.
%$\Box$
%\end{proof}

\textbf{Growth Factor} ($G_w^t$) is a parameter which declares
services' performance based on their recent strategies and
activities. Growth factor is relative to services' reputation
$Rep_w^t$, QoS during the window time $t$ $QoS_w^t$, and budget
$B_w^t$. This factor is the main variable a typical service uses
to decide about which strategy to adopt. We use Equation \ref{eq:growthfactor} to compute the
growth factor $G^t_w$ of the service $w$ during the window time
$t$ as the average of the three aforementioned parameters, where
$n_t$ is the total number of offered tasks to the whole community
during the
window time $t$, %(we consider the time window $t$ large enough so
%that $n_t \neq 0$),
$\mu_w$ is the mean received service fee, and $\epsilon$ is the
cost of community membership.

@@

  % if the profit $\beta_w$ made by the web service $w$
%considering the mean received service fee $\mu_w$ and the cost of
%community membership $\epsilon$ is positive.
%It is easy to show that Equation \ref{eq:growthfactor} satisfies
%the three aforementioned properties by calculating the partial
%derivatives $\partial G^t_w$ of this function in 1) $QoS_w^t$
%($\frac{\partial G^t_w}{\partial QoS_w^t} = \frac{1}{3} $); 2)
%$Rep^t_w$ ($\frac{\partial G^t_w}{\partial Rep^t_w} = \frac{1}{3}
%$); and 3) $B_w^t$ ($\frac{\partial G^t_w}{\partial B_w^t} =
%\frac{1}{3 (n_t \mu_w - \epsilon)} $). Thus, the sign of the two
%first partial derivatives is positive and the sign of
%$\frac{\partial G^t_w}{\partial B_w^t}$ depends on the sign of the
%maximum profit $n_t \mu_w - \epsilon$, so we are done.
The mean
service fee depends on the strategy adopted by the service because
a competitive service receives higher fees $\mu_{w, CM}$ compared
to a cooperative one $\mu_{w, CO}$ ($\mu_{w, CM} > \mu_{w, CO}$).
The motivation behind this is that a competitive service for a
given task is the leader for that task while other cooperative
services are performing specific subtasks as asked by the leader.

%\begin{proposition}\label{Complexity-Growth_Factor}
%$G_w^t$ can be computed in time linear in the size of the window
%$t$.
%\end{proposition}
%
%\begin{proof}
%As shown in the second part of Equation \ref{eq:growthfactor}, the
%function $QoS_w^t$ can be computed in time linear in the number of
%tasks, which in turn is linear in the size of the window time.
%Since $B_w^t$ is constant, the result follows from Proposition
%\ref{Complexity-Rep}. $\Box$
%\end{proof}

@@

In this section, we discuss the experiments we performed for our
scenarios to validate the applicability and performance of our
proposed methods in realistic environments.
An XML SOAP based messaging system was implemented. The request
contains the flight dates, the origin and destination, type of
tickets, and number of guests. The response contains different
flights with different companies, prices, timing, etc. We have
gathered around 200,000 flights and stored them in our MongoDB
database. We created a pool of web services and populated most of
their \emph{QoS} parameters from a real world web service dataset
\cite{DBLP:conf/smc/Al-MasriM09a}\footnote[1]{The implemented
environment includes the QWS dataset by Eyhab Al-Masri and Qusay
H. Mahmoud freely available at:
http://www.uoguelph.ca/\textasciitilde{}qmahmoud/qws/.}. To test
our methods, we formed around 10,000 random coalitions consisting
of 3 to 160 web services. In average, the communities were populated by 60 web
services. We implemented the
scenarios using Java and executed the experiments on an Intel Xeon
X3450 machine with 6GBs of memory.

@@

For the \emph{optimal core} method, we have used the well known
\emph{$\epsilon$-core} method as the taxation method to relax the
core condition to help communities attract web services. We have
assigned $\epsilon$ to 15\% of total community worth, which means
$\epsilon = 0.15 \times v(C)$. This allows subsets of the
coalition to gain maximum 15\% of $v(C)$. 
%In the \emph{optimal
%$\epsilon$-core} method, we capped the coalition size to 25 web
%services, since the method is computationally intractable as the
%number of web services increases. In fact, given the machine
%configuration we used in our experiments, the maximum number we
%could run for this method is 25, which is very realistic if we
%consider the real airlines coalitions (the three well known
%coalitions have respectively 28, 19, and 13 members). In the other
%methods, there were no cap on size of the community and we had
%communities of size 160 web services at some points, as discussed
%above.
In the experiments, our \emph{Depth-1 Convex-Checker} and
\emph{Depth-2 Convex-Checker} methods generate results instantly
(0.01ms in Java millisecond time unit granularity) in our machines
since their runtime with respect to the size of input (number of
web services) is $O(n)$ and $O(n^2)$ respectively. This shows that
the algorithms are efficient and the system is easily scalable. In
this scenario, our community receives 130 tasks from users on
average per iteration. These tasks are about flight booking and
are expected to be performed by the community. They are randomly
generated using a poisson distribution (having 130 as parameter).
Depending on community task queue and the assigned web services'
quality metrics the task will be performed with some qualities.
The community, after the task distribution process on each
iteration, will reevaluate QoS metrics of its members and can
check for new membership requests. Web services may join or leave
the community between iterations. The results show that our
\emph{depth-2 convex checker} method is performing better compared
to the other methods and its performance is close to the optimal
\emph{$\epsilon$-core} method. Our \emph{depth-1 convex checker}
and the \emph{3-Way Satisfaction} method, are also performing
well.

%
%\begin{figure*}%[!t]
%\centering
%%\includegraphics[scale=0.6]{graph1Final+.eps}
%\includegraphics[width=3in]{least_core.eps}
%\caption{Analysis of \emph{$\epsilon$-core} set non-emptiness for
%different values of $\epsilon$} \label{f_leastcore}
%\end{figure*}
%
%As mentioned in Section \ref{s:preliminaries}, the concept of
%\emph{core}, assumes no coalition of players can gain anything by
%deviating, which is a fairly strong requirement, and that is why
%the notion of \emph{$\epsilon$-core} was introduced. Least-Core
%$e(G)$ of a game $G$ is the minimum amount of $\epsilon$ so that
%the core is not empty. We evaluated the non-emptiness of
%\emph{$\epsilon$-core} set using our valuation function and a set
%of web services from our coalitions.  The restriction on the
%number of web services per coalition for this particular method is
%justified because it is
%very complex for larger coalitions to verify whether
%\emph{$\epsilon$-core} set is empty or not. Also instead of
%considering $\epsilon$ amount of constant deviation in
%\emph{$\epsilon$-core} definition (Equation \ref{eq:core2}), we    %TODO FIX THIS
%similarly defined \emph{relative $\epsilon$-core} concept where no
%coalition would benefit more than \emph{$\epsilon \times v(C)$} by
%deviating. We vary $\epsilon$ so that it takes different values
%from $0$ to $1$ and observe the impact in terms of verifying the
%\emph{relative $\epsilon$-core} set non-emptiness. The results in
%Figure \ref{f_leastcore} illustrate that almost 10\% of our random
%web service coalitions have non-empty \emph{core} solution and
%\emph{$\epsilon$-core} solution is \emph{always} non-empty when we
%let agents gain only 30\% more of $v(C)$ by deviating.
